---
title: "< STAT-5361 > HW#6"
author: "Hee-Seung, Kim"
date: "Oct 19, 2018"
output: pdf_document
fontsize: 11pt
documentclass: article
knit: "bookdown::render_book('HW6_Hee.Rmd','bookdown::pdf_document2')"
papersize: letter
biblio-style: asa 
---
 
\newpage
# Exercises 5.2.1

## (a)
As you can see following result, the g(x) can be expressed as a mixture of two Gamma distributions with different weights.
At first, we use that the integral result should be 1 for whole range;
$$\begin{aligned}
g(x)= c(2x^{\theta-1}+x^{\theta-\frac{1}{2}})e^{-x}
\end{aligned}$$
$$\begin{aligned}
c\int_{0}^{\infty}(2x^{\theta-1}+x^{\theta-\frac{1}{2}})e^{-x}dx
=c[2\int_{0}^{\infty}x^{\theta-1}e^{-x}dx+\int_{0}^{\infty}x^{\theta-\frac{1}{2}}e^{-x}dx]=1
\end{aligned}$$
Since $\Gamma(z)=\int_{0}^{\infty}x^{z-1}e^{-x}dx$ <- definition of Gamma function

$$\begin{aligned}
& 1) 2\int_{0}^{\infty}x^{\theta-1}e^{-x}dx = 2\Gamma(\theta)\\
& 2) \int_{0}^{\infty}x^{\theta-\frac{1}{2}}e^{-x}dx=\int_{0}^{\infty}x^{(\theta+\frac{1}{2})-1}e^{-x}dx
 =\Gamma(\theta+\frac{1}{2})\\
& \therefore  2\int_{0}^{\infty}x^{\theta-1}e^{-x}dx + \int_{0}^{\infty}x^{\theta-\frac{1}{2}}e^{-x}dx
 = 2\Gamma(\theta)+\Gamma(\theta+\frac{1}{2})=\frac{1}{c}\\
& c=\frac{1}{2\Gamma(\theta)+\Gamma(\theta+\frac{1}{2})}
\end{aligned}$$

in conclusion,
$$\begin{aligned}
g(x)&=c(2x^{\theta-1}+x^{\theta-\frac{1}{2}})e^{-x}
=\frac{1}{2\Gamma(\theta)+\Gamma(\theta+\frac{1}{2})}(2x^{\theta-1}+x^{\theta-\frac{1}{2}})e^{-x}\\
&=\frac{2\Gamma(\theta)}{2\Gamma(\theta)+\Gamma(\theta+\frac{1}{2})}(\frac{x^{\theta-1}e^{-x}}{\Gamma(\theta)})
+\frac{\Gamma(\theta+\frac{1}{2})}{2\Gamma(\theta)+\Gamma(\theta+\frac{1}{2})}(\frac{x^{(\theta+\frac{1}{2})-1}e^{-x}}{\Gamma(\theta+\frac{1}{2})})
\end{aligned}$$

## (b)
this function requires two parameters (N: desired number of sample, $\theta$: Gamma scale)


STEP 0. Prepare slots for the sample
        X <- rep(0,N);
        
STEP 1. Calculate the weight of each Gamma distribution ($\pi$ 1,$\pi$ 2)
        $\pi$ 1 <- 2 $\Gamma$($\theta$)/(2 $\Gamma$($\theta$)+$\Gamma$($\theta$+0.5))

STEP 2. For given N times,draw a Gamma observation according to the chosen index 
        for (i in 1:N) {
        if (runif(1) > $\pi$ 1) { X[i] <- r$\Gamma$(1,shape=$\theta$,scale=1)}
        else { X[i] <- r$\Gamma$(1,shape=$\theta$+0.5,scale=1)  }  }

STEP 3. Return generated values
        return(X);

```{r, echo=TRUE}
rs1b <- function(N,theta) {
  
  X <- rep(0,N);
  pi1 <- 2*gamma(theta)/(2*gamma(theta)+gamma(theta+0.5))
  pi2 <- 1-pi1
  
  for (i in 1:N) {
    if (runif(1) > pi1) { X[i] <- rgamma(1,shape=theta,scale=1)}
    else { X[i] <- rgamma(1,shape=theta+0.5,scale=1)  }
  }
  return(X);
}
rs1b(100,3)
```
  
## (c)
this function requires two parameters (N: desired number of sample, $\theta$: Gamma scale)

STEP 0. Prepare slots for the sample
X <- rep(0,N);

STEP 1. Draw a sample from g,using the rs1b function defined above.
        while (1) {
        Y = rs1b(1,$\theta$); 

STEP 2. If randomly generated uniform number exceed given thresh-hold,
        then sample Y again,o.w,retain Y.
        if (runif(1) < sqrt(4+Y)/(sqrt(Y)+2)) {
        X[i] = Y; break;
        }

STEP 3. Return generated values
        return(X);

```{r, echo=TRUE}
rs1c <- function(N,theta) {
  
  X <- rep(0,N);
  
  for (i in 1:N) {
    while (1) {
      Y = rs1b(1, theta); 
      if (runif(1) < sqrt(4+Y)/(sqrt(Y)+2)) {
        X[i] = Y; break;
      }
    }
  }
  return(X);
}

theta <- 2

sample1c <-rs1c(10000,theta)

## Estimate the density and compare it to q(x) to see if they are
## proportional to each other
## Specify on which interval the density function is to be estimated
intvl=c(.2, floor(max(sample1c)+1)+.2);

## Specify the number of points in the interval on which density is
## to be estimated.  The points are equally spaced in the interval,
## with the first one and last one being the end points of the interval
n.p=1+(intvl[2]-intvl[1])/0.02;

## Estimate the density.  The returned is a 
df.obj = density(sample1c, from=intvl[1], to=intvl[2], n=n.p)
x = df.obj$x;
df = df.obj$y;

## Calculate the value of q(x) 
q.val = (4+x)^0.5 * x^(theta-1)*exp(-x);

## Make the two on the same scale
q.val = q.val*mean(df)/mean(q.val);

plot(ts(cbind(df, q.val), start=intvl[1], deltat=diff(intvl)/(n.p-1)),
     plot.type="single", col=c("black", "red"),
     ylab="Density", xlab="x", 
     main = paste("5.2.1-c) Estimated density with 10,000 obs | theta:", theta));

legend('topright', legend=c("Simulated","Actual"),lty=c(1,1), 
       lwd=c(2.5,2.5),col=c('black','red'))
```




\newpage
# Exercises 5.2.2
## (a)
```{r}
rsa = function(n, theta, beta)
{
   ho = runif(n)
   number = sum( ho < beta(theta, 1)/( 2*beta(1, beta) + beta(theta, 1) ) )
   data = c(rbeta(number, theta, 1), rbeta(n-number, 1, beta))
   return(data)
}
algorithm3 = function(n, theta, beta)
{
   data = c()
   while( length(data) <= n )
   {
      ho = runif(1); x = rsa(1, theta, beta)
      q = (x^(theta - 1)/(1+x^2)) + sqrt(2+x^2)*(1-x)^(beta-1)
      g = x^(theta -1) + 2*(1-x)^(beta-1)
      if(ho <= q/g)
         data= c(data, x)
   }
   return(data)
}
theta = 1
beta = 1
integrand = function(x)
{
   (x^(theta - 1)/(1+x^2)) + sqrt(2+x^2)*(1-x)^(beta-1)
}
integral = integrate(integrand, 0, 1)
aa = algorithm3(10000, theta, beta)
hist(aa,freq=F,xlab='',main='')
lines(density(aa),col="red",lwd=4)
curve( ((x^(theta - 1)/(1+x^2)) + sqrt(2+x^2)*(1-x)^(beta-1))/as.numeric(integral[1]),
       add = T,col="blue",lwd=2)
legend('topright', legend=c("Simulated","Actual"),lty=c(1,1),
       lwd=c(2.5,2.5),col=c('green','blue'))
```

 
## (b)
```{r, echo=TRUE}
rsb = function(N, theta, beta)
{
  data = c()
  while(length(data) <= N )
  {
    d =sample(c(0,1),1)
    u = runif(1); 
    if(d == 0)
    {   
      ho = rbeta(1,theta, 1)
      q = (ho^(theta - 1)/(1+ho^2))
      g = ho^(theta -1) 
      if(u <= q/g)
        data= c(data, ho)
    }   
    else {
      x = rbeta(1, 1, beta)
      q = sqrt(2+ho^2)*(1-ho)^(beta-1)
      g = 2*(1-ho)^(beta-1)
      if(u <= q/g)
        data= c(data, ho)
    }
  }
  return(data)
}

theta = 1 
beta = 1

Func_ = function(x)
{
  (x^(theta - 1)/(1+x^2))+sqrt(2+x^2)*(1-x)^(beta-1)
}
integral = integrate(Func_, 0, 1)
tem = rsb(10000, theta, beta)
hist(tem,freq=F,xlab='',main='')
lines(density(tem),col="red",lwd=4)
curve( ((x^(theta - 1)/(1+x^2)) + sqrt(2+x^2)*(1-x)^(beta-1))/as.numeric(integral[1]),
       add = T,col="blue",lwd=2)
legend('topright', legend=c("Simulated","Actual"),lty=c(1,1),
       lwd=c(2.5,2.5),col=c('green','blue'))
```

